---
title: "Download Planet Imagery"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(jsonlite)
library(httr)
```

```{r}
api_key <- scan("planet-api-key", "")
```

API endpoints

```{r}
planet_api_URL <- "https://api.planet.com/data/v1/"
planet_stats_api <- 'https://api.planet.com/data/v1/stats'
planet_quicksearch_api <- 'https://api.planet.com/data/v1/quick-search'
```

Get item types, test API status
```{r}
r <- GET("https://api.planet.com/data/v1/item-types/")
http_status(r)
content(r)
```

Read in filter from json file

Still having problems creating the filter json using jsonlite

```{r}
search_combinedfilter <- jsonlite::read_json("search_combinedfilter.json")
toJSON(search_combinedfilter, pretty = TRUE)
```

Search API 

```{r}
r <- POST(planet_quicksearch_api,
          authenticate(api_key, password = ""),
          body = search_combinedfilter,
          encode = "json")
```

check status

```{r}
http_status(r)
```

```{r}
headers(r)
```

save returned content in an object

```{r}
r_content <- content(r)
sapply(r_content$features, function(x) x[["id"]])
```

## Activate asset for download

The search returns "items" which each have several "assets" which are the things you actually want to download

```{r}
str(r_content$features[[1]])
r_content$features[[1]]$id
r_content$features[[1]]$properties
```

Each item has an assets endpoint in the API that lists all of its assets.

Sent a GET request to the assets url. There must be a way to set authentication for the session so you don't need to put the authentication in again. 

```{r}
assets_url <- r_content$features[[1]]$`_links`$assets
r2 <- GET(assets_url, authenticate(api_key, password = ""))
http_status(r2)
content(r2) %>% names()
```

Look at the visual asset

```{r}
assets <- content(r2)
assets$visual
```

Send a request to the activation link 

```{r}
activation_url <- assets$visual$`_links`$activate
```

```{r}
r3 <- GET(activation_url, authenticate(api_key, password = ""))
http_status(r3)
```

Status codes 

* **202** - The request has been accepted and the activation will begin shortly.
* **204** - The asset is already active and no further action is needed.
* **401** - The user does not have permissions to download this file.

Once an asset is active, the response will contain a location. We'll use the location to download the asset!

Re-do the GET request to the asset url, which now has a location

```{r}
r2 <- GET(assets_url, authenticate(api_key, password = ""))
http_status(r2)
location_url <- content(r2)$visual$location
```

Download the file

```{r}
filename <- paste0("planet_download/", r_content$features[[1]]$id, ".tiff")
download.file(location_url, filename)
```

read in as a raster and plot

```{r}
library(raster)
jones <- raster(filename)
plot(jones)
```

