---
title: "Download Planet Imagery"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(jsonlite)
library(magrittr)
```

```{r}
# api_key <- scan("planet-api-key", "")
api_key <- scan("planet-api-key-nate", "")
# api_key <- scan("planet-api-key-cheng", "")
```

TODO - modify this to handle multiple images at once

API endpoints

```{r}
planet_api_URL <- "https://api.planet.com/data/v1/"
planet_stats_api <- 'https://api.planet.com/data/v1/stats'
planet_quicksearch_api <- 'https://api.planet.com/data/v1/quick-search'
```

# Download a specific asset based on item ID

Read in filter from json file (Still having problems creating the filter json using jsonlite)

Create a search JSON string based on an ID

```{r}
create_search_filter_3band <- function(idstring = "20171124_154939_0f29"){
  searchlist <- list(name = "PSScene3Band",
       item_types = list("PSScene3Band"),
       filter = list(
         type = "StringInFilter",
         field_name = "id",
         config = list(idstring)
       ))
  jsonlite::toJSON(searchlist)
  searchlist
}
```

```{r}
# imgIDs_enough_training <- readxl::read_excel("images_inventory/Planet Data.xlsx", sheet = "Planet_pipeline", skip = 1) %>%
#   dplyr::rename(enough_training = 9) %>%
#   dplyr::select(imgID, enough_training) %>%
#   dplyr::filter(enough_training) %>% dplyr::pull(imgID)
```

```{r}
# imgIDs_JL <- readr::read_csv("NDimgs.csv") %>% dplyr::pull(1)
```

```{r}
myimgs_nfs <- substr(basename(list.files("/Volumes/khondula-data/planetmethane/data/")), 1, 20)
myimgs_local <- substr(basename(list.files("download_sr/")), 1, 20)

# myudms <- substr(basename(list.files("download_udm/")), 1, 20)
# myxmls <- substr(basename(list.files("download_xml/")), 1, 20)

myimgs <- unique(c(myimgs_local, myimgs_nfs))

myvisuals_nfs <- substr(basename(list.files("/Volumes/khondula-data/planetmethane/metadata/download_visual")), 1, 20)
myvisuals_local <- substr(basename(list.files("download_visual/")), 1, 20)
myvisuals <- unique(c(myvisuals_local, myvisuals_nfs))
visuals_to_get <- myimgs[!myimgs %in% myvisuals]
visuals_to_get
# visuals_to_get <- imgIDs_enough_training[!imgIDs_enough_training %in% myvisuals]
# udms_to_get <-  myimgs[!myimgs %in% myudms]
# xmls_to_get <-  myimgs[!myimgs %in% myxmls]
# id_to_use <- xmls_to_get[1]
# id_to_use <- udms_to_get[1]
id_to_use <- visuals_to_get[1]
id_to_use
```

```{r}
search1 <- create_search_filter_3band(idstring = id_to_use)
# search1 <- create_search_filter(idstring = "20180930_152159_0f42")
# itemtype <- "analytic_sr"
# itemtype <- "udm"
# itemtype <- "analytic_xml"
itemtype <- "visual"

```

Search API 

```{r}
r <- POST(planet_quicksearch_api,
          authenticate(api_key, password = ""),
          body = search1,
          encode = "json")
```

save returned content in an object called `r`.

```{r}
r_content <- content(r)
feature_ids <- sapply(r_content$features, function(x) x[["id"]])
feature_ids
```

## Activate asset for download

```{r}
i = 1
assets_url <- r_content$features[[i]]$`_links`$assets
r2 <- GET(url = assets_url, config = authenticate(api_key, password = ""))
assets <- content(r2)
activation_url <- assets[[itemtype]]$`_links`$activate
activation_request <- GET(activation_url, authenticate(api_key, password = ""))
http_status(activation_request)
```

Once an asset is active, the response will contain a location. Use the location to download the asset.
Re-do the GET request to the asset url, which now has a location

```{r}
assets_url <- r_content$features[[i]]$`_links`$assets
r2 <- GET(url = assets_url, config = authenticate(api_key, password = ""))
location_url <- content(r2)[[itemtype]]$location
location_url
```

Download the file
```{r}
if(itemtype == "analytic_sr"){filename <- paste0("download_sr/", feature_ids[i], "_", itemtype, ".tiff")}
if(itemtype == "udm"){filename <- paste0("download_udm/", feature_ids[i], "_", itemtype, ".tiff")}
if(itemtype == "analytic_xml"){filename <- paste0("download_xml/", feature_ids[i], "_", itemtype, ".xml")}
if(itemtype == "visual"){filename <- paste0("download_visual/", feature_ids[i], "_", itemtype, ".tiff")}

download.file(location_url, filename)
```


