---
title: "Download Planet Imagery"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(jsonlite)
library(magrittr)
```

```{r}
# api_key <- scan("planet-api-key", "")
api_key <- scan("planet-api-key-nate", "")
# api_key <- scan("planet-api-key-cheng", "")
```

API endpoints

```{r}
planet_api_URL <- "https://api.planet.com/data/v1/"
planet_stats_api <- 'https://api.planet.com/data/v1/stats'
planet_quicksearch_api <- 'https://api.planet.com/data/v1/quick-search'
```

# Download a specific asset based on item ID

Read in filter from json file (Still having problems creating the filter json using jsonlite)

Create a search JSON string based on an ID

```{r}
create_search_filter <- function(idstring = "20171124_154939_0f29"){
  searchlist <- list(name = "PSScene4Band",
       item_types = list("PSScene4Band"),
       filter = list(
         type = "StringInFilter",
         field_name = "id",
         config = list(idstring)
       ))
  jsonlite::toJSON(searchlist)
  searchlist
}
```

```{r}
myimgs_nfs <- substr(basename(list.files("/Volumes/khondula-data/planetmethane/data/")), 1, 20)
myimgs_local <- substr(basename(list.files("download_sr/")), 1, 20)
# 
# myudms <- substr(basename(list.files("download_udm/")), 1, 20)
# myxmls <- substr(basename(list.files("download_xml/")), 1, 20)
# myvisuals <- substr(basename(list.files("download_visual/")), 1, 20)
# 
myimgs <- unique(c(myimgs_local, myimgs_nfs))
# 
# udms_to_get <-  myimgs[!myimgs %in% myudms]
# xmls_to_get <-  myimgs[!myimgs %in% myxmls]
# visuals_to_get <- myimgs[!myimgs %in% myvisuals]

# # id_to_use <- xmls_to_get[1]
# id_to_use <- udms_to_get[1]
# id_to_use <- visuals_to_get[1]
new_imgs_to_get <- imgs_to_get_noprobs$imgID[!imgs_to_get_noprobs$imgID %in% myimgs]
# id_to_use <- sample(new_imgs_to_get, 1)
id_to_use <- new_imgs_to_get[2]
id_to_use
```

```{r}
# search1 <- create_search_filter(idstring = id_to_use)
# 20171017_131703_0c82
# 20171017_131704_0c82
search1 <- create_search_filter(idstring = "20180713_151808_102c")
itemtype <- "analytic_sr"
# itemtype <- "visual"
# itemtype <- "udm"
# itemtype <- "analytic_xml"
```

Search API 

```{r}
r <- POST(planet_quicksearch_api,
          authenticate(api_key, password = ""),
          body = search1,
          encode = "json")
```

save returned content in an object called `r`.

```{r}
r_content <- content(r)
feature_ids <- sapply(r_content$features, function(x) x[["id"]])
feature_ids
```

## Activate asset for download

```{r}
i = 1
assets_url <- r_content$features[[i]]$`_links`$assets
r2 <- GET(url = assets_url, config = authenticate(api_key, password = ""))
assets <- content(r2)
activation_url <- assets[[itemtype]]$`_links`$activate
activation_request <- GET(activation_url, authenticate(api_key, password = ""))
http_status(activation_request)
```

Once an asset is active, the response will contain a location. Use the location to download the asset.
Re-do the GET request to the asset url, which now has a location

```{r}
assets_url <- r_content$features[[i]]$`_links`$assets
r2 <- GET(url = assets_url, config = authenticate(api_key, password = ""))
location_url <- content(r2)[[itemtype]]$location
location_url
```

Download the file
```{r}
if(itemtype == "analytic_sr"){filename <- paste0("download_sr/", feature_ids[i], "_", itemtype, ".tiff")}
if(itemtype == "udm"){filename <- paste0("download_udm/", feature_ids[i], "_", itemtype, ".tiff")}
if(itemtype == "analytic_xml"){filename <- paste0("download_xml/", feature_ids[i], "_", itemtype, ".xml")}
if(itemtype == "visual"){filename <- paste0("download_visual/", feature_ids[i], "_", itemtype, ".tiff")}


download.file(location_url, filename)
```


